\bf ISODS: An ISODATA-Based Initial Centroid Algorithm

### 2021-01-11 paper/paper.tex
add hyper links

\documentclass[a4paper, 10pt]{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{\bf ISODS: An ISODATA-Based Initial Centroid Algorithm}
\author{Noah Gardner$^1$, Sahar Yarmohammadtoosky$^2$, \\
      Anthony Phan$^3$, and Chih-Cheng Hung$^4$\\[1ex]
      \sl \small Kennesaw State University, Marietta, GA, USA$^{1, 3, 4}$\\
      \sl \small Iran University of Science and Technology, Tehran,
      Iran$^2$\\[1ex]
      \small $^1$ngardn10@students.kennesaw.edu, \small
      $^2$yarmohamadishr@gmail.com, \\
      \small $^3$aphan5@students.kennesaw.edu, \small $^4$chung1@kennesaw.edu,
      \\}
\date{}
\maketitle

@@

This method began as a modified ISODATA process. However, the modification was
unique in that there is a clear distinction from the proposed change and the
beginning of the original process. Although more complex than other methods of
generating initial cluster centers, this approach guarantees variance between
clusters. As a result, ISODS can be used to generate clusters for other
clustering algorithms, such as K-Means.

@@

\begin{table}[ht]
      \caption{Salinas-A dataset average and best results over 1000 iterations
            of ISODATA comparing three different initial cluster center
            algorithms (\textit{Init.}).}
      \begin{tabular}{ |p{1.25cm}||p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm}|}
            \hline
            \multicolumn{7}{|c|}{\textbf{ISODATA} - \textit{Salinas-A}}        \\
            \hline
            Init. & Iter. & Clusters & ARI            & RI    & MI    & HI     \\
            \hline
            \multicolumn{7}{|c|}{\textit{Average}}                             \\
            \hline
            ISODS & 2.772 & 2.42     & \textbf{0.156} & 0.388 & 0.612 & -0.224 \\
            KM++  & 3.177 & 1.097    & 0.019          & 0.228 & 0.772 & -0.544 \\
            Rand  & 3.693 & 1.584    & 0.084          & 0.308 & 0.691 & -0.383 \\
            \hline
            \multicolumn{7}{|c|}{\textit{Best}}                                \\
            \hline
            ISODS & 2     & 6        & 0.758          & 0.921 & 0.078 & 0.842  \\
            KM++  & 8     & 6        & 0.781          & 0.930 & 0.070 & 0.860  \\
            Rand  & 14    & 6        & \textbf{0.798} & 0.933 & 0.066 & 0.867  \\
            \hline
      \end{tabular}
      \label{tab:salinastable}
\end{table}

\begin{figure}[ht]
      \centering
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{salinasgt.png}
            \label{fig:salinasgt}
      \end{subfigure}
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{risodata.png}
            \label{fig:salinasr}
      \end{subfigure}
      \centering
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{kisodata.png}
            \label{fig:salinask}
      \end{subfigure}
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{iisodata.png}
            \label{fig:salinasi}
      \end{subfigure}\hfill \caption{Heatmap showing cluster assignments of each
            pixel using ISODATA with different initial cluster center methods.
            (a) Salinas-A Ground Truth; (b) Random Centers (ARI=0.797); KM++
            Centers (ARI=0.781); ISODS Centers (ARI=0.758).}
      \label{fig:salinas}
\end{figure}

>>>>

\documentclass[a4paper, 10pt]{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}

@@

\title{\bf ISODS: An ISODATA-Based Initial Centroid Algorithm}
\author{
      Noah Gardner$^1$,
      Sahar Yarmohammadtoosky$^2$, \\
      Anthony Phan$^3$,
      and Chih-Cheng Hung$^4$\\[1ex]
      \sl \small Kennesaw State University, Marietta, GA, USA$^{1, 3, 4}$\\
      \sl \small Iran University of Science and Technology, Tehran,
      Iran$^2$\\[1ex]
      \small \href{mailto:ngardn10@students.kennesaw.edu}{$^1$ngardn10@students.kennesaw.edu},
      \small \href{mailto:yarmohamadishr@gmail.com}{$^2$yarmohamadishr@gmail.com}, \\
      \small \href{mailto:aphan5@students.kennesaw.edu}{$^3$aphan5@students.kennesaw.edu},
      \small \href{mailto:chung1@kennesaw.edu}{$^4$chung1@kennesaw.edu} \\
}
\date{}
\maketitle

@@

This method began as a modified ISODATA process. However, the modification was
unique in that there is a clear distinction from the proposed change and the
beginning of the original process. Although more complex than other methods of
generating initial cluster centers, this approach guarantees separation between
clusters. As a result, ISODS can be used to generate clusters for other
clustering algorithms, such as K-Means.

@@

\begin{table}[ht]
      \caption{Salinas-A dataset average and best results over 1000 iterations
            of ISODATA comparing three different initial cluster center
            algorithms (\textit{Init.}). ARI - adjusted Rand index; RI - Rand
            index; MI - Mirkin's index; HI - Hubert's index.}
      \begin{tabular}{ |p{1.25cm}||p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm} p{1.25cm}|}
            \hline
            \multicolumn{7}{|c|}{\textbf{ISODATA} - \textit{Salinas-A}}        \\
            \hline
            Init. & Iter. & Clusters & ARI            & RI    & MI    & HI     \\
            \hline
            \multicolumn{7}{|c|}{\textit{Average}}                             \\
            \hline
            ISODS & 2.772 & 2.42     & \textbf{0.156} & 0.388 & 0.612 & -0.224 \\
            KM++  & 3.177 & 1.097    & 0.019          & 0.228 & 0.772 & -0.544 \\
            Rand  & 3.693 & 1.584    & 0.084          & 0.308 & 0.691 & -0.383 \\
            \hline
            \multicolumn{7}{|c|}{\textit{Best}}                                \\
            \hline
            ISODS & 2     & 6        & 0.758          & 0.921 & 0.078 & 0.842  \\
            KM++  & 8     & 6        & 0.781          & 0.930 & 0.070 & 0.860  \\
            Rand  & 14    & 6        & \textbf{0.798} & 0.933 & 0.066 & 0.867  \\
            \hline
      \end{tabular}
      \label{tab:salinastable}
\end{table}

\begin{figure}[ht]
      \centering
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{salinasgt.png}
            \caption{}
            \label{fig:salinasgt}
      \end{subfigure}
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{risodata.png}
            \caption{}
            \label{fig:salinasr}
      \end{subfigure}
      \centering
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{kisodata.png}
            \caption{}
            \label{fig:salinask}
      \end{subfigure}
      \begin{subfigure}[b]{0.24\textwidth}
            \centering
            \includegraphics[width=\linewidth]{iisodata.png}
            \caption{}
            \label{fig:salinasi}
      \end{subfigure}\hfill \caption{Heatmap showing cluster assignments of each
            pixel using ISODATA with different initial cluster center methods.
            (a) Salinas-A Ground Truth; (b) Random Centers (ARI=0.798); KM++
            Centers (ARI=0.781); ISODS Centers (ARI=0.758).}
      \label{fig:salinas}
\end{figure}
